When are Fuzzy Extractors Possible?

### 2015-01-08 trunk/info-bounds/FuzzyExtPossibility.tex
working on new proof outline for leveled hashing

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hoo(W)= m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell-1$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.  Define $\sketch_W, \rec_W$ as: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $ss=1,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $ss =0,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss)$
\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, y, K) = ss_{1,..., |y|}$.
\item $W^* = \{w \in \supp(W) | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
\item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\section{Proof of \thref{thm:layered hashing}}
\label{sec:proof of layered hashing}
\begin{proof}
Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.
We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
\[
\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | w\in \supp(W) \wedge \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
\]

@@

\noindent
\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.

The best strategy for an adversary that receives $i$ as is to guess a point that has the most nearby weight in that level.  The adversary chooses 
\[
w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | 2^{-(i+1)}< \Pr[W=w]\le 2^{-i}\wedge \dis(w, w')}\Pr[W=w].
\] 
The success of this adversary is at least $2^{-(i+1)}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at least $2^{-(i+1)}$.  There are $n$ outcomes for $i$. The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-(i+1)}\beta_{t,i}&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W| 2^{-(i+1)}< \Pr[W=w]\le 2^{-i} \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
&= n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
\bnote{need to clean up this proof}
We now argue security.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align*}
\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\\
&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)
\end{align*}
For the remainder of the proof, we seek a bound on 
\[
2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0} = \max_{w\in W | 2^{-(n+m)}<\Pr[W=w]}\Pr[W=w | \sketch(W)].
\]
We separate out this quantity into levels:\bnote{we need to talk about K here}\bnote{we were asked what $\Pr[W=w| \sketch(W)]$ means, to me that's well formed}\bnote{shouldn't there be a term here $\Pr[L_i = i]$?}
\begin{align*}
\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &\ge -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}

>>>>

\begin{construction}
\label{cons:leveling}
Let $\mathcal{M}$ be a metric space and let $n =\log |\mathcal{M}|$. Let $W$ be a distribution with $\Hoo(W)= m$.  Let $\ell\in\mathbb{Z}^+$ be a parameter.  Let $L_i = (2^{-(i+1)}, 2^{-i}]$ for $i=m,..., m+\ell-1$.  Let $F_i :\mathcal{K}_i\times \mathcal{M}\rightarrow R_i$ be a parameterized family of universal hash functions.  Define $\sketch_W, \rec_W$ as: 
\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{$\sketch_W$}
\begin{enumerate}
\item \underline{Input}: $w$.
\item If $\Pr[W=w] \le 2^{-(m+\ell)}$. Set $ss=1,w$.
\item Else
\begin{enumerate}
\item Find $i$ such that $\Pr[W=w]\in L_i$.
\item Sample $K\leftarrow \mathcal{K}_i$.
\item Set $ss =0,  i, F_i(K, w), K$.
\end{enumerate}
\end{enumerate}
\vspace{.4in}
\end{minipage} &
\begin{minipage}{3.5in}
\textbf{$\rec_W$}
\begin{enumerate}
\item \underline{Input}: $(w', ss)$
\item If $ss_0 = 1$, output $ss_{1,..., |y|}$.
\item Else
\begin{enumerate}
\item Parse $(i, y, K) = ss_{1,..., |y|}$.
\item $W^* = \{w | \dis(w, w')\le t \\\, \, \, \wedge \Pr[W=w]\in L_i\}$.
\item For $w^*\in W^*$, if $F_i(K, w^*) = z$, \\ output $w^*$.
\item Output $\perp$.
\end{enumerate}
\end{enumerate}
\end{minipage}
\end{tabular}
\end{center}
\end{construction}

@@

\section{Proof of \thref{thm:layered hashing}}
\label{sec:proof of layered hashing}
\begin{proof}
Throughout the proof we assume that $\ell = n$ is the number of levels.  The proof can be carried out for an arbitrary $\ell$ but it leads to a complicated theorem statement.
We extend our notation for the maximum likelihood ball to the leveled case.  Define $\beta_{t,i}$ as the maximum number of points in a ball in level $i$.  That is,
\[
\beta_{t,i} = \max_{w' \in \mathcal{M}} \left|\{w | \dis(w, w')\le t \wedge \Pr[W=w]\in L_i\}\right|.
\]

@@

\bnote{new outline to proof. proof to come}
\begin{enumerate}
\item show chain rule for fuzzy min-entropy
\item show that fuzzy min-entropy conditioned on i is related to $\beta_{t, i}$.
\item show that releasing the sketch only gives delta more than necessary.
\end{enumerate}
\noindent
\textbf{Ideal Adversary with access to Level Information:} To aid in the argument in security, we show the level information on its own is not too harmful.  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.

Let $I$ be the random variable describing the level.  Since there are at most $n$ outcomes for the level when $1_{\text{low}} =0$, we have that \[\Hav( W | I \wedge 1_{\text{low}}=0) \ge \Hoo(W) -\log n.\]

In the standard secure sketch game, to maximize probability of predicting $w$, the adversary supplies the $w'$ with the most nearby probability mass.  With the additional information about the probability of $w$, the adversary should supply $w'$ with the most nearby probability in the correct probability level.  That is, the adversary's best guess is:
\[
w^*= \argmax_{w' \in \mathcal{M}}\sum_{w\in W | \Pr[W=w]\in L_i\wedge \dis(w, w')}\Pr[W=w].
\] 
The success of this adversary is at most $2^{-i}\beta_{t,i}$ as there at $\beta_{t,i}$ nearby points in that layer each with probability at most $2^{-i}$.  There are $n$ outcomes for $i$. The overall success of such an adversary is at most $n$ better than an adversary without such input~(by~\cite[Lemma 2.2]{DBLP:journals/siamcomp/DodisORS08}).  That is, 
\begin{align}
\expe_{i | m\le i \le m+n}2^{-i}\beta_{t,i}%&\le \expe_{i | m\le i \le n+m}\left( \max_{w^*\in W}\sum_{w\in W|  w\in L_i \wedge \dis(w, w^*) \le t}\Pr [W=w]\right) \nonumber\\
%&\le n \left(\max_{w^*\in W} \sum_{w\in W | \dis(w, w^*)\le t} \Pr[W=w]\right)\nonumber \\
&\ge n 2^{-\Hfuzz(W)}\label{eq:link fuzz 3}
\end{align}
\textbf{Security:}
We just saw that an adversary that learns $L_i$ performs at most a factor of $n$ better than an adversary without this information.  We now argue security of the construction.  First note that the total weight of points whose probability is less than $2^{-(n+m)}$ is at most $2^{-m}$~(there are at most $2^n$ points in the distribution).  Let $1_{\text{low}}$ be the indicator random variable for $\Pr[W=w]\le 2^{-(n+m)}$.  Then 
\begin{align}
\Hav(W | \sketch(W)) &= -\log \left(\Pr[1_{\text{low}}=1] * 1 + \Pr[1_{\text{low}} =0]   2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\right)\nonumber\\
&\ge -\log\left( 2^{-m} + (1-2^{-m})2^{-\Hav(W | \sketch(W) \wedge 1_{\text{low}} = 0)}\label{eq:min-entropy}\right)
\end{align}
For the remainder of the proof, we seek a bound on $\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0).$

Let $L_I$ denote the random variable denoting the probability of $\Pr[W=w]$.
All the dependence between $W$ and $K$ is contained in $L_I$.   That is, $\Hav(W | K_I , L_I) = \Hav(W | L_I)$. Let $Y_I$ denote the outcome of the hash function.  We now consider the remaining average min-entropy when $1_{\text{low}} = 0$:
\begin{align*}
\Hav(W | \sketch(W) \wedge 1_{\text{low}} =0) &= \Hav(W | L_I , K_I, Y_I \wedge 1_{\text{low}}=0)\\
&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | K_i , Y_i, i)}\right)\right)\\
&= -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(2^{-\Hav(W | Y_i, i)}\right)\right)\\
&\ge -\log \left(\expe_{i\leftarrow L_I | m \le i \le m+n} \left(\frac{(\beta_{t, i}-1)}{\delta}2^{-\Hav(W | i)}\right)\right)\\
&= -\log \left(\frac{1}{\delta}\left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i)}\right)\right)\right)\\
&= -\log \left(\frac{2}{\delta} \left( \expe_{i\leftarrow L_I | m \le i \le m+n} \left(\beta_{t, i}2^{-(i+1)}\right)\right)\right)\\
&= -\log \left(\frac{2n}{\delta} 2^{-\Hfuzz(W)}\right)\\
\end{align*}
Where the first inequality proceeds by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}
\begin{align*}
\max_{w\in W | 2^{-(m+n)}< \Pr[W=w]}\left(\Pr[W=w | \sketch(W)]\right) &= \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w | \sketch(W), i]\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\max_{w\in W | \Pr[W=w]\in L_i} \Pr[W=w]\cdot 2^{H_0(\sketch(W) | i)}\right)\\
&\le \expe_{i | m\le i \le m+n} \left(\frac{2^{-i}*\beta_{t,i}}{\delta}\right)\\
&\le\frac{ \expe_{i | m\le i \le m+n} \left(2^{-(i+1)}\cdot \beta_{t,i}\right)}{2\delta}\\
%&=\delta \sum_{i | m\le i \le m+n} \Pr[W\in L_i]\left(2^{-i}*\beta_{t,i}\right)
%\end{align*}
%Now consider This allows us to conclude that 
%\begin{align*}
%\max_{w\in W | \Pr[W=w]>2^{-n}\epsilon}\left(\Pr[W=w | \sketch(W)]\right) 
&= \frac{n 2^{-\Hfuzz(W)}}{2\delta}.
\end{align*}
Where the last line follows by Equation~\eqref{eq:link fuzz 3}.
Combining both cases we have:
\begin{align*}
\Hav(W | \sketch(W)) &\ge -\log \left(2^{-m}+\frac{(1-2^{-m})(n)2^{-\Hfuzz(W)}}{2\delta}\right)\\
&\ge -\log \min\{2^{-m}, \frac{(1-2^{-m}) n2^{-\Hfuzz(W)}}{2\delta}\})-1\\
&\ge \Hfuzz(W) - \log n + \log \delta - \log (1-2^{-m}) - 2\\
&\ge \Hfuzz(W) - \log n + \log \delta - 3\\
\end{align*}
Where the third line follows from the second because $\Hfuzz(W)\le \Hoo(W) = m$. The last line follows from the fourth because if $m\ge 1$ then $\log (1-2^{-m})\le 1$ and if $m< 1$ the entire bound is vacuous as $\Hfuzz(W)< 1$.
\end{proof}
